--- 
title: "FluvialGeomorph User Manual"
date: "`r Sys.Date()`"
author: 
  - Michael Dougherty, Geographer, US Army Corps of Engineers, Rock Island District
  - Christopher Haring, Geomorphologist/Research Physical Scientist, Coastal Hydraulics Laboratory, U.S. Army Corps of Engineers
  - Davi Michl, Biologist, US Army Corps of Engineers, Rock Island District
site: bookdown::bookdown_site
output: bookdown::gitbook
documentclass: book
bibliography: [book.bib, packages.bib]
biblio-style: chicago
link-citations: true
description: "This user manual describes how to use FluvialGeomorph for stream analysis."
---

```{r include=FALSE}
library(knitr)
library(png)
```

# {-}
See the [Guide for Preparing Technical Information Reports of the Engineer Research and Development Center](http://www.dtic.mil/dtic/tr/fulltext/u2/a445281.pdf) for details on ERDC Technical Report development. 


## Abstract
The abstract appears on the reverse side of the title page. It summarizes
the research problem, project objective, and outcome of the investigation.
It should run no more than 200 words. 


## Disclaimer
Also on the reverse side of the title
page is the standard disclaimer of any implied government endorsement
of products discussed in text. 


## Distribution Statement
The distribution statement is a critical component of both the cover and
the title page. Every ERDC technical publication must be imprinted with
one of the seven primary distribution statements required by Department
of Defense Directive (DoDD) 5230.24. A distribution statement constitutes
ERDC’s decision on who is authorized to read the report. Most reports
published by ERDC are intended for unrestricted public access and carry
Statement A: “Approved for public release; distribution is unlimited.”
However, access to many reports may need to be restricted for reasons
ranging from proprietary information content to national security interests
related to militarily critical technology. Appendix B presents the text
of every nonclassified distribution statement and the approved justifica-
ERDC/ITL SR-04-1 8
tions for applying each one. Only reports labeled with Statement A shall be
posted to the World Wide Web for unrestricted public access. 


## Preface
A preface is included in all ERDC reports to present essential nontechnical
documentation of the research project, such as funding authorization,
sponsorship, technical contributors to project execution, chain of
supervision, and the authors’ acknowledgments. Figure A3 presents a
sample showing all the required elements. 


## Unit Conversion Factors
A unit conversion factors table is included in all reports that do not use
metric units or dual units. The table should include only those U.S. customary
units used in the report. It should be compiled from the master list
of conversion factors maintained by PTTB. For more information, see
“Expressing and converting units of measure” (page 14). 


## Notation List
A notation list also may be included to define characters, symbols, and abbreviations used to express technical facts or quantities. It appears after
the unit conversion factors. Figure A4 presents a formatted sample. @R-base


```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```
